method

### 2022-02-09 06_Paper/ER-ED/method.Rmd
updated BF of ANOVAS

---
output: html_document
bibliography: ER_ED.bib
csl: apa7.csl
---

@@

# Bayes Factors
SubjArousalView_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
                                           data = Ratings_reg,
                                           progress = FALSE)

@@

# figure
FigPilot2 = ggplot2::ggplot(Ratings_reg, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")

@@

# ANOVA subjective effort ratings

effort_reg = data_ER %>%
  subset(data_ER$block != "view_neu" & data_ER$block != "choice")

aov.effort = afex::aov_ez(data = effort_reg,
                          id = "ID",
                          dv = "effort",
                          within = "block",
                          fun_aggregate = mean,
                          include_aov = TRUE)
#afex::nice(aov.effort, es = "pes")

# compute posthoc tests for within measure
posthoc_effort = emmeans::emmeans(aov.effort$aov, specs = "block")
#pairs(posthoc_effort, adjust = "bonferroni")

# Figure to visualize effort ratings
# figure
FigPilot3 = ggplot2::ggplot(effort_reg, aes(x = block, y = effort))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Effort Rating")
```

@@

The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED.
According to the 21-word-solution, "we report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012].
A complete list of all measures assessed in the study will be found at the OSF (https://osf.io/vnj8x/) and GitHub (github.com/ChScheffel/COG-ER-ED). <!-- Attention! OSF is still private -->
All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.

@@

The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants ()

@@

Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS) [@Lang2008]. 
The 20 neutral pictures (Valence (V): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$valence), digits = 2)` $\pm$ `r round(sd(stim_neutral$valence), digits = 2)`; Arousal (A): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$arousal), digits = 2)` $\pm$ `r round(sd(stim_neutral$arousal), digits = 2)`) depicted content related to the categories persons, objects, and scenes.
Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used. 
An evolutionary algorithm [@Yu2010] was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
A complete list of all pictures and their classification into sets can be found in supplementary material X.

@@

Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. <!--JZ: Das stand oben schon mal-->
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Sample size calculation is done using *G\*Power* [@Faul2007; @Faul2009].
In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported.  
To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of least $N=85$ have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of 90 participants.

>>>>

---
output: html_document
bibliography: ER_ED.bib
csl: apa7.csl
editor_options: 
  markdown: 
    wrap: sentence
---

@@

# Bayes Factors
SubjArousalReg_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
                                           data = Ratings_reg,
                                           progress = FALSE)

@@

# figure
FigPilot2 <- ggplot2::ggplot(Ratings_reg, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")

@@

SubjEffort_aov <- afex::aov_ez(data = Ratings_reg,
                          id = "ID",
                          dv = "effort",
                          within = "block",
                          fun_aggregate = mean,
                          include_aov = TRUE)

# compute posthoc tests for within measure
SubjEffort_emm <- emmeans::emmeans(SubjEffort_aov$aov, specs = "block")

SubjEffort_con <- as.data.frame(pairs(SubjEffort_emm, adjust = "bonferroni"))

# Bayes Factors
SubjEffort_BF <- BayesFactor::anovaBF(formula = effort ~ block,
                                           data = Ratings_reg,
                                           progress = FALSE)

SubjEffort_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "view_neg"],
                                                                         y = Ratings_reg$effort[Ratings_reg$block == "distraction"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "view_neg"],
                                                                         y = Ratings_reg$effort[Ratings_reg$block == "distancing"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "view_neg"],
                                                                         y = Ratings_reg$effort[Ratings_reg$block == "suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "distraction"],
                                                                         y = Ratings_reg$effort[Ratings_reg$block == "distancing"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "distraction"],
                                                                         y = Ratings_reg$effort[Ratings_reg$block == "suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "distancing"],
                                                                         y = Ratings_reg$effort[Ratings_reg$block == "suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf)

SubjEffort_con$etasq <- format(effectsize::t_to_eta2(t = SubjEffort_con$t.ratio,
                                                         df_error = SubjEffort_con$df,
                                                         ci = 0.95),
                                   digits = 2)

# Figure to visualize effort ratings
# figure
FigPilot3 = ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Effort Rating")
```

@@

The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED.
According to the 21-word-solution, "we report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012].
A complete list of all measures assessed in the study will be found at the OSF (<https://osf.io/vnj8x/>) and GitHub (github.com/ChScheffel/COG-ER-ED).
<!-- Attention! OSF is still private --> All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.

@@

The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`\text{ }\pm\text{ }SD = `r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$).

@@

Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS) [@Lang2008].
The 20 neutral pictures (Valence (V): *M* $\pm$ *SD* = `r round(mean(stim_neutral$valence), digits = 2)` $\pm$ `r round(sd(stim_neutral$valence), digits = 2)`; Arousal (A): *M* $\pm$ *SD* = `r round(mean(stim_neutral$arousal), digits = 2)` $\pm$ `r round(sd(stim_neutral$arousal), digits = 2)`) depicted content related to the categories persons, objects, and scenes.
Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used.
An evolutionary algorithm [@Yu2010] was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
A complete list of all pictures and their classification into sets can be found in supplementary material X.

@@

Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
<!--JZ: Das stand oben schon mal--> Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Sample size calculation is done using *G\*Power* [@Faul2007; @Faul2009].
In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported.\
To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of least $N=85$ have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of 90 participants.
